Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-09-11 manuscript/accessPEP.Rmd
moved manuscript files to sep directory
also changed rmd so that directory defaults to the .Rproj directory

---
title: "Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar"
author: ""
date: 
output:
  html_document: default
  pdf_document:
    includes:
      in_header: mystyle.sty
  word_document:
    reference_docx: format_docs/word_styles_reference_01.docx
---

@@

## Travel times
ttimes <- raster("output/ttimes_masked.tif")
gg_SD <- fortify(SD_shape, region = "VILLCODE")

@@

## baseline proportion
threshold = 3 # threshold # of hours to calculate the proportion of pop at
sum(prop_pop[ttimes >= 60*threshold], na.rm = TRUE)
sum(prop_pop[ttimes_best >= 60*5], na.rm = TRUE)

@@

@@

ggplot(results_all_base, 
       aes(y = deaths_mean/pop*1e5, x = reorder_within(names, by = covar, within = covar_name), 
                              color = model)) +
  geom_pointrange(aes(ymin = deaths_lowerCI/pop*1e5, ymax = deaths_upperCI/pop*1e5), fatten = 2) +
  xlab("Districts ordered by access \n (high to low)") +
  ylab("Annual deaths per 100k persons") +
  coord_flip() +
  scale_color_manual(values = c(alpha("navy", 0.5), alpha("purple", 0.5)), 
                     name = "Scale") +
  scale_x_reordered() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~covar_name, scales = "free_y") +
  labs(tag = "A") -> d

>>>>

---
title: "Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar"
author: ""
date: 
output:
  html_document: default
  pdf_document:
    includes:
      in_header: format/mystyle.sty
  word_document:
    reference_docx: format/word_styles_reference_01.docx
---

@@

## Travel times
ttimes <- raster("output/ttimes_masked.tif")

@@

## baseline proportion
threshold = 3 # threshold # of hours to calculate the proportion of pop at
sum(prop_pop[ttimes >= 60*threshold], na.rm = TRUE)
sum(prop_pop[ttimes_best >= 60*3], na.rm = TRUE)

@@

### Figure from 538
distance_summ <- bind_rows(distance_dist, distance_comm)
distance_summ %>%
  group_by(scenario, names, model, covar_name) %>%
  summarize(deaths_mean = sum(deaths_mean, na.rm = TRUE), 
            deaths_upperCI = sum(deaths_upperCI, na.rm = TRUE),
            deaths_lowerCI = sum(deaths_lowerCI, na.rm = TRUE),
            averted_mean = sum(averted_mean, na.rm = TRUE), 
            averted_upperCI = sum(averted_upperCI, na.rm = TRUE),
            averted_lowerCI = sum(averted_lowerCI, na.rm = TRUE), 
            covar = mean(covar, na.rm = TRUE))   %>%
  left_join(dist_data, by = c("names" = "district")) %>%
  drop_na(names) -> distance_summ

(sum(distance_comm$deaths_mean)/sum(distance_comm$pop))*1e5

ggplot(data = distance_summ, 
       aes(y = deaths_mean/pop*1e5, x = reorder_within(names, by = covar, within = covar_name))) +
  geom_point(data = distance_comm, 
             aes(y = deaths_mean/pop*1e5, x = reorder_within(names, by = covar, within = covar_name)), 
             shape = 16, color = "#3a9679", alpha = 0.5) + 
  geom_point(shape = 22, aes(fill = model), color = "black", alpha = 1, size = 2.5) +
  xlab("Districts ordered by access \n (high to low)") +
  ylab("Annual deaths per 100k persons") +
  geom_hline(yintercept = 1, color = "black", linetype = 2) + 
  scale_fill_manual(values = c(alpha("#3a9679", 1), alpha("#e4c666", 1)), 
                     name = "Scale") +
  scale_x_reordered() +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        panel.grid.major.y = element_line(color = alpha("grey", 0.25)), 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x = element_blank(), 
        panel.background = element_rect(fill = "white")) +
  # facet_wrap(~covar_name, scales = "free_y") +
  labs(tag = "A")

@@

ggplot(results_all_base, 
       aes(y = deaths_mean/pop*1e5, x = reorder_within(names, by = covar, within = covar_name), 
                              color = model)) +
  geom_pointrange(aes(ymin = deaths_lowerCI/pop*1e5, ymax = deaths_upperCI/pop*1e5), fatten = 2) +
  xlab("Districts ordered by access \n (high to low)") +
  ylab("Annual deaths per 100k persons") +
  coord_flip() +
  scale_color_manual(values = c(alpha("#3a9679", 1), alpha("#e4c666", 1)), 
                     name = "Scale") +
  scale_x_reordered() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~covar_name, scales = "free_y") +
  labs(tag = "A") -> d
